QPLIB: A Library of Quadratic Programming Instances

### 2018-02-02 AnswerToTheReferees.tex

\item I think it would be interesting to mention the Conic library CBLIB \url{http://cblib.zib.de} and its relation to the library described in the manuscript.

\rep{We updated the manuscript by adding the suggest link to the Conic library.}

\item Page 7, line -4. You say that convex means that the feasible region is
convex, but in page 19 you discuss the fact that SOCP problems that have
a convex feasible region could be considered nonconvex. Hence, maybe it
is more accurate to say that what you mean is that the constraint can be
converted to $f (x) \le c$ with $f$ convex by rearranging terms.

\rep{We removed a sentence from this paragraph to address this concern
%TODO: Leo 
%\leo{secondo me il secondo commento si riferisce a pagina 19... a pagina 7 riga -4 non trovo niente su SOCP. Pero` sono d'accordo che a pagina 19 l'ultimo paragrafo della sezione 3.1 potrebbe essere migliorato. Cosi` e` un po' criptico. Perche' non inserire un bell'esempio di una forma bilineare nonconvessa (scrivendola esplicitamente come xQx e dando esplicitamente lo spettro di Q con la parte definita negativa) inserita in un vincolo che definisce una regione convessa? E poi io direi che facciamo la scelta di mettere queste istanze come "nonconvesse" perche' dimostrare convessita` in generale e` difficile (a questo proposito, io conosco i risultati del PhD di Amir Ali Ahmadi sulla difficolta` di riconoscere la convessita` in polinomi di grado $>= 4$, ma non ho mai visto una dimostrazione di difficolta` di riconoscere la convessita` della feasible region in vincoli quadratici; spero che qualcuno dei nostri co-autori ne sia al corrente)... Il referee ricorda che riconoscere i casi di forme quadratiche con una negative eigenvalue inserite in un vincolo convesso e` facile e  da` un metodo, di cui sarebbe bene ritrovare il primo caso in cui viene menzionato, oppure darne una breve dimostrazione... io non ne ero a conoscenza (e nemmeno mi viene in mente sui due piedi come dimostrarlo).} 
}

@@

\item The y-axis labels are missing on most figures.

\rep{
TODO: Stefan and Ambros
%\leo{mettiamo la label al y axis  (duh)} 
}

\item Reword the sentence ``percentage of ``hard'' eigenvalues'', p.23, l.-6. The notion of hard has a
special meaning in trust-region problems. Also, this is not a measure of hardness, as explained
above. Instead, you should consider the number of negative eigenvalues of the reduced Hessian
(wrt equality constraints). Fig. 4 is meaningless, unless you replace the definition of hardness.

\rep{
We renamed ``hard" to ``problematic". However, as explained in \S 2.2.1 and 2.2.2, we refrain from reformulating the instance, and we do not tailor problems to specific solvers (moreover, not all QP solvers would resort to reduced Hessians). In the same vein, our analysis can only be based on the given instance structure.
%TODO: Stefan and Ambros.
% \leo{non so nulla di "hard eigenvalues" nel senso del trust region; chiediamo agli esperti} 
 }

### 2018-02-02 AnswerToTheReferees.tex

\rep{[\dots] }

{\it
\begin{enumerate}

\item There are two classes of important missing application domains of QPs in Table 1: (1) trust-region subproblems, and (2) PDE-constrained optimization problems. In fact, there exist a number of PDE-constrained instances in CUTEr, which would be useful additions to the library. The authors should add at least a few such examples. the lack of these problems is worrying, because
it (implicitly) assumes that direct solvers are used, which means that this library is less relevant for matrix-free solvers.

\rep{
Thank you for pointing out the missing categories. As requested, we updated Table 1 with the two required Applications.
We also included PDE-constrained instances in the updated version of the library.
We have deliberately excluded the highly-specialized class of trust-region subproblems, since there are dedicated, very fast solvers for this class. See for example:
\begin{itemize}
\item
Minimizing a quadratic over a sphere. \\
W. W. Hager. 
SIAM Journal on Optimization,12(1):188-208, 2001.
\item
Solving the trust-region subproblem using the Lanczos method. \\
N. I. M. Gould, S. Lucidi, M. Roma, and Ph. L. Toint. 
SIAM Journal on Optimization, 9(2):504-525, 1999.
\item
A semidefinite framework for trust region subproblems with applications to large scale minimization.\\
F Rendl, H Wolkowicz.
Mathematical Programming 77 (1), 273-299
\item
A Subspace Minimization Method for the Trust-Region Step.\\
J. B. Erway and P. E. Gill.
SIAM J. Optim. 20-3 (2010), pp. 1439-1461
\item
Solving the Trust-Region Subproblem By a Generalized Eigenvalue Problem.\\
S. Adachi, S. Iwata, Y. Nakatsukasa and A Takeda.
SIAM Journal on Optimization 27 (1), 269-291
\item
On solving trust-region and other regularised subproblems in optimization.\\
N.I.M. Gould, D.P. Robinson and H.S. Thorne.
Mathematical Programming Computation 2 (1), 21-57
\end{itemize}
%\leo{sono d'accordo, dovremmo aggiungere delle istanze da trust-region subproblem e delle istanze da problemi PDE-constrained. Chiediamo a Gould per le istanze trust-region e a Gould, Mittelmann e Sahinidis per PDE-constrained. Specifichiamo che vorremmo istanze NON gia` in CUTE.} 
}

### 2018-02-03 QPLIB-2.2.tex
Update QPLIB-2.2.tex

\Leo{\sout{Following the remark of one of our anonymous referees,} We note that, although the left-to-right progression in the above text marks ``harder problems'', this does \textit{not} mean that \textit{every} instance of a hard problem is itself ``difficult to solve''. As is well known, problems as infinite collections of instances; and it is always possible to find subclasses that can be solved efficiently.}

>>>>

\Leo{We note that, although the left-to-right progression in the above text marks ``harder problems'', this does \textit{not} mean that \textit{every} instance of a hard problem is itself ``difficult to solve''. As is well known, problems as infinite collections of instances; and it is always possible to find subclasses that can be solved efficiently.}
